\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx}
\begin{document}

	\begin{center}
		{\huge\textbf{MAKERERE UNIVERSITY}}\\
		{\large\textbf{COLLEGE OF COMPUTING AND INFORMATION SCIENCES}}\\
		\textbf{SCHOOL OF COMPUTING AND INFORMATICS TECHNOLOGY}\\
		\textbf{DEPARTMENT OF COMPUTER SCIENCE}
	\end{center}
	GROUP 6 COURSE WORK\\
	COURSE UNIT : RESEARCH METHODOLOGY\\
	INSTRUCTOR : EARNEST MWEBAZE\\
	COURSE CODE : BIT 2207\\



\begin{tabular}{|p{5cm} |p{3cm}|p{3cm}|p{3cm}|}
\hline
\multicolumn{4}{|c|}{Group 6}\\
\hline
\hline
Name & Registration Number & Student Number&Signature\\
\hline
MATOVU GEOFREY&16/U/6902/EVE&216008997&\\
BAMANYE&16/U/4206/EVE&216013268&\\
KAJJOBA MUDASILU&16/U/5198/EVE&216015944&\\
SADALA BADRU ATULINDA&16/U/3901/EVE&216010207\\
\hline

\end{tabular}
\section{HARD DISK FAILURE DETECTOR}
\subsection{Introduction}
The aim of this document is to provide a high light of how hard drive failure prediction can be improved and summarize a range of literature to highlight themes and generate recommendations for future work in this area by Hard Drive Failure Predictor. This section contains the background which purposely describes the origin of hard disk failure and points out past and recent studies, problem statement pointing out research gaps, objectives and scope of the study. It will help clarify to the reader how fulfillment of the research aims and objectives will improve on data storage through effective hard drive failure detection. In addition the document will partitioned into other sections which include the literature review, research methodology timeframe, risks and project budget inclusive.  
\section{PROBLEM STATEMENT}
Data loss especially in developing countries has been a major problem affecting both novice or occasional users and expert users. This is due to the fact that second hand equipment are being imported 95% in these countries. This has led to abrupt disk crashes where Banking institutions, web hosting companies, data centers and personal users have lost vast data beyond recovery. 
Hard disk failure predictor will be a phone based software which will be  a solution to this problem where  all users will use their mobile phones to compute the health status and  durability of  their  logic drives in hardware shops, web hosting companies, banking institutions, homes and any other data storage related institutions. 
\section{OBJECTIVES}
\subsection{GENERAL OBJECTIVE}
To create a system that will effectively predict hard drive defects or failure.
\subsection{SPECIFIC OBJECTIVES}
To critically asses how users maintain and use their hard drives.
To recommend users to detect and predict hard disk failure and maximize data backup.
To evaluate and classify operations of data recovery schemes by different users.





\end{document}



